---
title: "R-Programming For Statistics"
author: "Anirban Maity, M.Sc (Statistics), University of Kalyani"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    highlight: tango
    theme: journal
    number_sections: yes
---

**Basics of R**

*Recipe - 1: Creating vectors*
```{r}
# Creating vectors
a = c(12, 10, "ANIRBAN", 12.56)
paste("The vectors are")
# print(a)
a
```

*Recipe-2: Creating List*
```{r}
# Print list of Strings i.e., list of names
list_1 = list("Anirban", "Tapomoyee", "Ankan", "Debarati", "Subhadeep", "Neha")
list_1

# Print list of Ages
list_2 = list(22,22,23,24,23,25)
list_2
```

*Recipe-3: Creating Matrix*
```{r}
num = c(1,2,3,4,5,6,7,8,9)
mat = matrix(num, nrow = 3, ncol = 3, byrow = TRUE)
mat
```

*Recipe-4: Creating Array*
```{r}
# Creating two matrix each of order 2x3
Array = array(1:12, dim = c(2,3,2))
Array
```

*Recipe-5: Choosing Specific element from creating vector*
```{r}
a = c(12, 10, "ANIRBAN", 12.56)
# Choosing 3rd element from the vector
a[3]
```

*Recipe-6: Choosing Specific element from list*
```{r}
list_1 = list("Anirban", "Tapomoyee", "Ankan", "Debarati", "Subhadeep", "Neha")
# Choosing 2nd element from the creating list
list_1[[2]]
```

*Recipe-7: Choosing Specific element from matrix*
```{r}
num = c(1,2,3,4,5,6,7,8,9)
mat = matrix(num, nrow = 3, ncol = 3, byrow = TRUE)
mat

# Selecting 2nd and 3rd Column
mat[,c(2,3), drop = FALSE]

# Selecting 2nd and 3rd row 
mat[c(2,3),,drop = FALSE]

# Selecting element 5,6,8,9 from the matrix
mat[c(2,3),c(2,3)]
```

*Recipe-8: Choosing Elements from Array*
```{r}
Array = array(1:12, dim = c(2,3,2))
Array
# Selecting 1st row from the 2nd matrix
Array[1,,2]

# Selecting 2nd column from 2nd matrix
Array[,2,2]

# Selecting 1st, 3rd column from 1st matrix
Array[, c(1,3), 1]
```

*Recipe-8: Creating Dataframe*
```{r}
Name = c("Anirban", "Tapomoyee", "Ankan", "Debarati", "Subhadeep", "Neha")
Age = c(22,22,23,24,23,25)
Sex = c("M", "F", "M", "F", "M", "F")
frame = data.frame(Name, Age, Sex)
frame
knitr::kable(frame)
```
*Recip-9: Selecting Age column from the created dataframe*
```{r}
Age_data = frame$Age
Age_data
```

*Recipe-10: Selecting 2nd row from the dataframe*
```{r}
frame[2,]
```

*Recipe-11: Subsetting from data frame using subset() function*
```{r}
# Selecting only female Category data from the above created data frame
female_data = subset(frame, Sex == "F")
female_data

#Selecting only female category data whose age greater than 22
female_data_age = subset(frame, c(Sex == "F" & Age>22))
female_data_age
```

*Recipe-12: Inserting an element in the creating vector, list*
```{r}
# Inserting another name in the created vector after 3rd position
a = c(12, 10, "ANIRBAN", 12.56)
append(a, "Tapomoyee", after = 3)

# Inserting new name Nilanjana in the list_1, after 5th position
list_1 = list("Anirban", "Tapomoyee", "Ankan", "Debarati", "Subhadeep", "Neha")
append(list_1, "Nilanjana", after = 5)

# Inserting new number in the list_2, after 5th position
list_2 = list(22,22,23,24,23,25)
append(list_2, 22, after = 5)
```

**Decision control Structure**

*Q1. Program to find wheather you are eligible for vote or not*
```{r}
name = readline(prompt = "Enter Your Name: ")
Age = readline(prompt = "Enter Your Age: ")
if(Age>=18)
{
  print("You are eligible for vote")
} else
{
  print("You are not eligible for vote")
}
```

**Loop Structure**

*Q1. Program to print 1st 10 natural numbers using While loop*
```{r}
i = 1 # initialization
while(i<=10) # Condition
{
  print(i) # Instruction to do
  i = i + 1 # Update information
}
```

*Q2. Program to print sum of 1st 10 natural numbers using While loop*
```{r}
i = 0 # initialization-1
s = 0 # Initialization-2
while(i<=10) # Condition 
{
  s = s + i # Instruction
  i = i + 1 # Update information
}
paste("The sum of 1st 10 natural numbers is ", s)
```

*Q3. Program to print sum of numbers between m and n using While loop*

```{r}
m = as.numeric(readline(prompt = "Enter the value of m = "))
n = as.numeric(readline(prompt = "Enter the value of n = "))
s = 0
while(m<=n)
{
  s = s + m
  m = m + 1
}
paste("The sum of the numbers is = ", s)
```

*Q4. Program to print 1st 10 natural numbers using for loop*
```{r}
for(i in 1:10)
{
  print(i)
  i = i + 1
}
```

*Q5. Program to print sum of 1st 10 natural numbers using for loop*
```{r}
s = 0
for(i in 1:10)
{
  s = s + i
  i = i + 1
}
paste("The sum of 1st 10 natural numbers = ", s)
```

*Q6. Program to print sum of numbers between m and n using for loop*
```{r}
m = as.numeric(readline(prompt = "Enter the value of m = "))
n = as.numeric(readline(prompt = "Enter the value of n = "))
s = 0
for(i in m:n)
{
  s = s + m
  m = m + 1
}
paste("The sum of numbers = ", s)
```
*Q7. Program to print sum of arbitrary input numbers*
```{r}
num = scan()
s = 0
for(i in 1: length(num))
{
  s = s + num[i]
  i = i + 1
}
paste("The sum of the numbers = ", s)
```

*Q8. Program to create a data frame*
```{r}
library(magicfor) # magicfor library used to find out the result from the loop structure. this library has various functions which are used to magicalize the for loop
magic_for(silent = TRUE)
num1 = scan()
x = num1
num2 = scan()
f = num2

for(j in 1:length(x))
{
  prod_val = x[j]*f[j]
  i = i + 1
  put(prod_val)
}
xf = magic_result_as_vector()
w = 0
for(i in 1:length(f))
{
  w = w + f[i]
  i = i + 1
  put(w)
}
F = magic_result_as_vector()
frame1 = data.frame(x, f, F, xf)
colnames(frame1)<- c("Values(x)", "Frequency(f)", "Cumulative Frequecy(< type)", "xf")
knitr::kable(frame1)
```

```{r}
frame1
```

*Q9. Program to print odd position number*
```{r}
num = c(10,12,14,13,15,25,28,23,26,24,27)
for(i in 1:length(num))
{
  if(i%%2!=0)
  {
    print(num[i])
  }
}
```



```{r}
mat = matrix(c(1,2,3,4), 2, 2, byrow = TRUE)
mat
```

```{r}
mat[,1]
mat[,1, drop = FALSE]
```

